### 2021-09-01 documentos/pce.tex
agrego generadores linblad, me falta la derivacion, mas detalels

The construction of quantum channels includes basically three ingredients: linearity, trace preserving and complete positivity. The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ with $\rho \in \mcS(\hilbert)$.
\subsection{Single qubit case} % {{{
% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
% mapas proyectivos, hay mapas proyectivos no unitales}
\todo{David escribe una primera version y luego Carlos itera}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}

>>>>

The construction of quantum channels includes basically three ingredients: linearity, trace preserving and complete positivity. The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete positivity condition is needed to preserve positive semidefiniteness and handle the non-local character of quantum theory. This is, with positivity of the map $\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with $\Delta\geq 0$. In the other hand, complete positvity of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state between the system and an ancilla with Hilbert space $\hilbert_k$. Therefore, complete positivity ensures that every positive semidefinite operator of any extension of the system (where the quantum channel is now a local operation) is mapped into positive semidefinite operators, trace preserving is automatically fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system where $\mcE$ acts locally, is send to a valid density matrix, this is the substance of complete positivity.

Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\sa g
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i
\end{equation}

with
\begin{equation}
\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
\label{eq:1qubit_semigroup}
\end{equation}
We will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
\begin{equation}
\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
\label{eq:Nqubit_semigroup}
\end{equation}

\begin{align}
U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
\label{eq:1qubit_stinespring}
\end{align}
similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
\label{eq:Nqubit_stinespring}
\end{align}

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}
